Constructing a Convolutional Neural Network from ground up

### 2023-05-31 doc/paper.tex
Theory part finished
Signed-off-by: Gregz9 <gregorkajda@gmail.com>

>>>>

Note that the Convolution2DLayer takes in an activation function as a parameter, as it also performs non-linearity.

\subsubsection{Backpropagation in the convolutional layer}
As you may have noticed, we have not yet explained how the backpropagation algorithm works in a convolutional layer. However, having covered all other major details about convolutional layers, we are now prepared to do so. It should come as no surprise that the calculation of delta terms at each convolutional layer takes the form of convolution. After the gradient has been propagated backwards through the flattening layer, where it was reshaped into an appropriate form, calculating the update value for the kernel is simply a matter of convolving the output gradient with the input of the layer for which we are updating the weights. For more detail, this article serves as an excellent resource \href{https://pavisj.medium.com/convolutions-and-backpropagations-46026a8f5d2c}{\color{blue}Convolutions\ and\ backpropagations}

\subsubsection{Format of input data}
Note that image data usually comes in many different shapes and sizes, but for our CNN we require the input data be formatted as [Number of inputs, input channels, input height, input width]. Occasionally, the data you come accross use will be formatted like this, but on many occasions reshaping and transposing the dimensions is sadly necessary.

\subsection{Optimized Convolution2DLayer}
or our CNN, we have also implemented an optimized version of the Convolution2DLayer (following guidance from [Weidman, A. Deep Dives], although many modifications had to be made), Convolution2DLayerOPT, which runs much faster. See VII. Remarks for discussion. This layer will per default be used by the CNN due to its computational advantages, but is much less readable. We've documented it such that specially interested students can understand the principles behind it, but it is not recommended to read. In short, we reshape and transpose parts of the image such that the convolutional operation can be swapped out for a simple matrix multiplication.

\subsection{Pooling Layer}
The pooling layer is a commonly used layer in convolutional neural networks (CNNs) that facilitates downsampling of data to a more manageable size. Despite advancements in convolution techniques that preserve data size, the pooling layer remains a fundamental component of CNNs. It can be positioned before, after, or between convolutional layers, and the optimal arrangement and network depth depend on experimental evaluation to achieve the best performance for a given problem. Our provided code allows for two types of pooling: max pooling and average pooling. In max pooling, the value of a pixel at coordinates $(x,y)$ is determined by selecting the maximum value among the pixels in a window extracted in the same manner as before convolution. On the other hand, average pooling extracts the window and computes the new pixel's intensity as the average intensity of the pixels in that window.

\subsection{Flattening Layer}
Before we can begin building our first CNN model, we need to introduce the flattening layer. As its name suggests, the flattening layer transforms the data into a one-dimensional vector that can be fed into the feedforward layers of our network. This layer plays a crucial role in preparing the data for further processing in the network. Additionally, the flattening layer is responsible for reshaping the gradient to the proper shape during backpropagation. This ensures that the kernels are correctly updated, allowing for effective learning in the network.
